Verifying Demonstrations

### 2018-05-30 paper/DistanceBounding.tex
Capitalize DB frauds in list

The main attacks against \ac{DB} protocols can be summarized as follows:
%Seb: the following names of attacks should all have the first letters in capital
\begin{itemize}
  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

>>>>

The main attacks against \ac{DB} protocols can be summarized as follows:
%Seb: the following names of attacks should all have the first letters in capital
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \Acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
